USAMS Hybrid Source Summary

### 2021-02-01 hgis_summary.Rmd
Update notes and summary with most recent data.

@@

@@

A: Unknown. We should look at variability between identical samples to get a sense of reproducibility. Some data are available, but no controlled replicates have been run.

@@

* Repeated measurements under identical conditions to determine reproducibility
* Test breakthrough with new open split
* Establish best helium flow for displacement
* Fine tune capillary length for best flow to source over pCO2 range of full size sample
* How to handle < 1 Atm in vials. Backfill?
* Measure test samples prepped on Gilson (7mL CO2, Atm pressure)
* Define blank, determine whether current-balance correction is needed.
* Refine normalization and error propagation for data reduction.

@@

>>>>

Source currents are variable by day and by target. "Good" currents for a given day vary between 5-10uA, and it's not yet clear what causes this variability. Alignment, source condition, and settings of the ionizer and cesium are all factors. Current also varies by target for a given set of gas and source conditions. Some targets are clearly "bad", producing currents much lower than other targets for a given set of conditions.

@@

Measurement of a small number of replicates shows that between sample reproducibility is around 1%. Samples displaced by helium have slightly higher variability, but more tests are needed to better assess reproducibility.

@@

A: Initial data from identical samples run under similar conditions show standard deviation of around 1-1.5% for modern samples.

@@

* More repeated measurements under identical conditions to determine reproducibility
* Test breakthrough with new open split
* Establish best helium flow for displacement
* Fine tune capillary length for best flow to source over pCO2 range of full size sample
* How to handle < 1 Atm in vials. Backfill?
* Measure test samples prepped on Gilson (7mL CO2, Atm pressure)
* Define blank, determine whether current-balance correction is needed.
* Refine normalization and error propagation for data reduction.

@@

2021-01-29 - Ran a series of vial tests with modern and dead CO2 to assess reproducibility.
